ME780 Assignment 1

### 2016-02-12 homework/homework_1/report.tex
Update report

\begin{equation}
	Q = 
	\begin{bmatrix}
		0.5 & 0 & 0 \\
		0 & 0.5 & 0 \\
		0 & 0 & 10		
	\end{bmatrix}
\end{equation}

With a mean $\mu$ of:

@@

Where $G_{t}$ is the first order differential of the non-linear motion model. 
We have, however, omitted the differentiation because we already know what 
$G_{t}$ is, since we have already derived the differential of $g(x_{t-1}, 
u_{t})$ in Section~\ref{sec:motion_model_derivation}.

\begin{equation}
	G_{t} = \dot{g}(\theta, \omega) = R(\theta)^{-1} J_{1}^{-1} J_{2} \omega
\end{equation}

@@

\begin{align}
	R(\theta) &= 
 	\begin{bmatrix}
	    \cos{(\theta)} & -\sin{(\theta)} & 0 \\
	    \sin{(\theta)} & \cos{(\theta)} & 0 \\
	    0 & 0 & 1
    \end{bmatrix} \\
	J_{1} &= 
	\begin{bmatrix}
			0 & 1 & l \\
  	    	-\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l \\
   	    	\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l
    \end{bmatrix} \\
    J_{2} &=
    \begin{bmatrix}
        r & 0 & 0 \\
        0 & r & 0 \\
        0 & 0 & r
    \end{bmatrix} \\
    \omega &= 
	    \begin{bmatrix}
	       \omega_{1} \\
	       \omega_{2} \\
	       \omega_{3} \\
	    \end{bmatrix}
\end{align}

\begin{equation}
	G_{t} = \dot{g}(\theta, \omega) =
	\begin{bmatrix}
		\frac{2}{3} \sin(\theta) r \omega_{1}
			- \frac{1}{\sqrt{3}} \cos(\theta) r \omega_{2}
				- \frac{1}{3} \sin(\theta) r \omega_{2}
			+ \frac{1}{\sqrt{3}} \cos(\theta) r \omega_{3}
				- \frac{1}{3} \sin(\theta) r \omega_{3} \\ \\
		\frac{2}{3} \cos(\theta) r \omega_{1}
			+ \frac{1}{\sqrt{3}} \sin(\theta) r \omega_{2}
				-\frac{1}{3} \cos(\theta)r \omega_{2}
			- \frac{1}{\sqrt{3}} \sin(\theta) r \omega_{3}
				-\frac{1}{3} \cos(\theta) r \omega_{3} \\ \\
		\frac{1}{3l} r \omega_{1}
			+ \frac{1}{3l} r \omega_{2}
			+ \frac{1}{3l} r \omega_{3}
	\end{bmatrix}
\end{equation}

@@

\begin{align*}
	\mu_{0} &= 
		\begin{bmatrix}
			0 \\
			0 \\
			0
		\end{bmatrix} \\
	u_{0} &= 
	\begin{bmatrix}
		-15.5 \\
		-10.5 \\
		1.5
	\end{bmatrix} \\
	H_{t} &=
	\begin{bmatrix}
		1 & 0 & 0 \\
		0 & 1 & 0 \\
		0 & 0 & 1
	\end{bmatrix} \\
	G_{t} &= \dot{g}(\theta, \omega) \\
		&= R(\theta)^{-1} J_{1}^{-1} J_{2} \omega
	    \begin{bmatrix}
	        \dot{x} \\
	        \dot{y} \\
	        \dot{\theta}
	    \end{bmatrix} \\
	    &= 
	        \begin{bmatrix}
		        \cos{(\theta)} & -\sin{(\theta)} & 0 \\
		        \sin{(\theta)} & \cos{(\theta)} & 0 \\
		        0 & 0 & 1
	        \end{bmatrix}^{-1}
	        \begin{bmatrix}
	            0 & 1 & l \\
	          	-\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l \\
	        	\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l
	        \end{bmatrix}^{-1}
	        \begin{bmatrix}
	            r & 0 & 0 \\
	            0 & r & 0 \\
	            0 & 0 & r
	        \end{bmatrix}
		    \begin{bmatrix}
		       \omega_{1} \\
		       \omega_{2} \\
		       \omega_{3} \\
		    \end{bmatrix} \\
\end{align*}

>>>>

\begin{equation}
	Q = 
	\begin{bmatrix}
		0.5 & 0 & 0 \\
		0 & 0.5 & 0 \\
		0 & 0 & 0.1745		
	\end{bmatrix}
\end{equation}

Note that 10 degrees is 0.1745 radians. With a mean $\mu$ of:

@@

Where $G_{t}$ is the first order differential of the non-linear motion model, 
a.k.a the Jacobian of $g(x_{t-1}, u_{t})$.

\begin{equation}
	G_{t} = \begin{bmatrix}
		\dfrac{\partial g_{1}}{\partial x_{1}}
		& \dfrac{\partial g_{1}}{\partial x_{2}} 
		& \dfrac{\partial g_{1}}{\partial x_{3}} \\ \\
		\dfrac{\partial g_{2}}{\partial x_{1}}
		& \dfrac{\partial g_{2}}{\partial x_{2}} 
		& \dfrac{\partial g_{2}}{\partial x_{3}} \\ \\
		\dfrac{\partial g_{3}}{\partial x_{1}}
		& \dfrac{\partial g_{3}}{\partial x_{2}} 
		& \dfrac{\partial g_{3}}{\partial x_{3}}
	\end{bmatrix}
\end{equation}

Since we only know $\dot{g}(\theta, \omega)$ we need to convert it to 
$g(x_{t-1}, u_{t})$, it is simply:

\begin{align}
	g(x_{t-1}, u_{t}) 
		&= x_{t - 1} + \dot{g}(\theta, \omega) dt \\
		&= \begin{bmatrix}
			x_{1, t - 1} + \dot{g_{1}}(\theta, \omega) dt \\ \\
			x_{2, t - 1} + \dot{g_{2}}(\theta, \omega) dt \\ \\
			x_{3, t - 1} + \dot{g_{3}}(\theta, \omega) dt \\
		\end{bmatrix}
\end{align}

Now that we have $g(x_{t-1}, u_{t})$ we can work out the Jacobian. One 
important note, the partial derivate of $x_{3}$ in our case is the bearing  
$\theta$ of the robot, the only term affected in $\dot{g}(\theta, \omega)$ is 
the rotation matrix $R(\theta)$, since $\dot{g}(\theta, \omega)$ is:

\begin{equation}
    \dot{g}(\theta, \omega) = R(\theta)^{-1} J_{1}^{-1} J_{2} \omega
\end{equation}

@@

\begin{align}
	R(\theta)^{-1} &= 
 	\begin{bmatrix}
	    \cos{(\theta)} & \sin{(\theta)} & 0 \\
	    -\sin{(\theta)} & \cos{(\theta)} & 0 \\
	    0 & 0 & 1
    \end{bmatrix} \\
	J_{1}^{-1} &= 
	\begin{bmatrix}
		0 & -\frac{1}{\sqrt{3}} & \frac{1}{\sqrt{3}} \\ \\
		\frac{2}{3} & -\frac{1}{3} & -\frac{1}{3} \\ \\
		\frac{1}{3l} & \frac{1}{3l} & \frac{1}{3l}
	\end{bmatrix} \\
    J_{2} &=
    \begin{bmatrix}
        r & 0 & 0 \\
        0 & r & 0 \\
        0 & 0 & r
    \end{bmatrix} \\
    \omega &= 
	    \begin{bmatrix}
	       \omega_{1} \\
	       \omega_{2} \\
	       \omega_{3} \\
	    \end{bmatrix}
\end{align}

Therefore to differentiate rotation matrix $R(\theta)$ with respect to $x_{3}$ 
(or $\theta$), we can treat $J_{1}$ $J_{2}$ and $\omega$ as constant vector 
$A$. The partial derivative of $R(\theta)$ then becomes:

\begin{equation}
	\dfrac{\partial R(\theta)^{-1}}{\partial x_{3}} = 
	\begin{bmatrix}
		-\sin(x_{3}) & \cos(x_{3}) & 0 \\ \\
		-\cos(x_{3}) & -\sin(x_{3}) & 0 \\ \\
		0 & 0 & 0
	\end{bmatrix}
\end{equation}

\begin{equation}
	A = J_{1}^{-1} J_{2} \omega
\end{equation}

Or in terms of $g$ and $x$.

\begin{align}
	\dfrac{\partial g}{\partial x_{3}} 
	&= \dfrac{\partial R(\theta)^{-1}}{\partial x_{3}} A \\
	&= \begin{bmatrix}
		-\sin(x_{3}) & \cos(x_{3}) & 0 \\
		-\cos(x_{3}) & -\sin(x_{3}) & 0 \\
		0 & 0 & 0
	\end{bmatrix}
	\begin{bmatrix}
		A_{1} \\
		A_{2} \\
		A_{3}
	\end{bmatrix} \\
	&= \begin{bmatrix}
		-A_{1} sin(x_{3}) + A_{2} cos(x_{3}) \\
		-A_{1} cos(x_{3}) - A_{2} sin(x_{3}) \\
		0
	\end{bmatrix}
\end{align}

Completing our Jacobian $G_{t}$ we get:

\begin{equation}
	G_{t} = \begin{bmatrix}
		1 & 0 & -A_{1} sin(x_{3}) + A_{2} cos(x_{3})  \\
		0 & 1 & -A_{1} cos(x_{3}) - A_{2} sin(x_{3}) \\
		0 & 0 & 1
	\end{bmatrix}
\end{equation}

@@

\begin{align*}
	\mu_{0} &= 
		\begin{bmatrix}
			0 \\
			0 \\
			0
		\end{bmatrix} \\
	u_{0} &= 
	\begin{bmatrix}
		-15.5 \\
		-10.5 \\
		1.5
	\end{bmatrix} \\
	H_{t} &=
	\begin{bmatrix}
		1 & 0 & 0 \\
		0 & 1 & 0 \\
		0 & 0 & 1
	\end{bmatrix} \\
	G_{t} 
		&= \begin{bmatrix}
			1 & 0 & -A_{1} sin(x_{3}) - A_{2} cos(x_{3})  \\
			0 & 1 & A_{1} cos(x_{3}) - A_{2} sin(x_{3}) \\
			0 & 0 & 1
		\end{bmatrix} \\
	    &= 
	        \begin{bmatrix}
		        \cos{(\theta)} & -\sin{(\theta)} & 0 \\
		        \sin{(\theta)} & \cos{(\theta)} & 0 \\
		        0 & 0 & 1
	        \end{bmatrix}^{-1}
	        \begin{bmatrix}
	            0 & 1 & l \\
	          	-\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l \\
	        	\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l
	        \end{bmatrix}^{-1}
	        \begin{bmatrix}
	            r & 0 & 0 \\
	            0 & r & 0 \\
	            0 & 0 & r
	        \end{bmatrix}
		    \begin{bmatrix}
		       \omega_{1} \\
		       \omega_{2} \\
		       \omega_{3} \\
		    \end{bmatrix} \\
\end{align*}
